\noindent{

Neural networks are all the rage with the kids these days. News articles are constantly published about how neural nets are being applied with staggering results to image recognition, speech recognition, image synthesis, pattern recognition and other problems.
}

This paper does not mean to provide an in-depth analysis of the best possible approach for a given method. Instead this papers seeks to compare the performance characteristics and ease of use of a simple feed-forward neural network implementation to random forests. We conduct experiments against a dataset containing yelp reviews for a classification and a regression task.

Our dataset consists of yelp reviews of which the count of 50 different words in the review are given without any contextual information. The regression task consists of predicting how many people found a review useful based on the labeled training data. The classification task consists of trying to predict wether the review received over 3 "stars" from other users of the service.

Experiments are conducted against these tasks to compare the performance characteristics and other properties of these two very different methods.

This paper is laid out in several sections. In section ~\ref{sec:methods} a general overview of the compared methods is given. Section ~\ref{sec:experiments} describes the experiments performed and section ~\ref{sec:results} presents the results of the experiments. Section ~\ref{sec:discussion} gives a short discussion of the results.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "report"
%%% End:

